An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps

### 2019-01-04 algorithm_radix.Rmd
Radix format

---
title: "An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps"
author: "Stephanie"
date: "6 December 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Abstract

>>>>

---
title: "An algorithm for a spatial mapping using a hexagon tilegram, with application to Australia disease maps"

author:
  - name: Stephanie Kobakian
    url: https://github.com/srkobakian
    affiliation: Queensland University of Technology
date: "`r Sys.Date()`"
output: radix::radix_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Abstract
